COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries, and Implications for Messaging

### 2021-05-04 paper_files/figure-latex/fig2paper-1.tex
drop drive calls
update
no google drive
paper
update files

% Created by tikzDevice version 0.12.3.1 on 2021-03-23 16:52:30
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 87.69, 67.14) --
	( 87.69,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.09, 67.14) --
	(101.09,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (114.48, 67.14) --
	(114.48,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (127.88, 67.14) --
	(127.88,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.00, 67.14) --
	( 81.00,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.39, 67.14) --
	( 94.39,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.79, 67.14) --
	(107.79,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.18, 67.14) --
	(121.18,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,137.15) --
	(111.16,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.16,139.95) --
	( 94.55,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.55,137.15) --
	( 94.55,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,445.18) --
	(105.80,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (105.80,447.98) --
	(100.02,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.02,445.18) --
	(100.02,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,417.18) --
	(101.14,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.14,419.98) --
	( 94.07,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.07,417.18) --
	( 94.07,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,361.17) --
	( 90.75,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.75,363.97) --
	( 81.16,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 81.16,361.17) --
	( 81.16,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,333.17) --
	( 94.66,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.66,335.97) --
	( 90.37,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 90.37,333.17) --
	( 90.37,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,305.16) --
	( 97.50,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 97.50,307.96) --
	( 89.09,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.09,305.16) --
	( 89.09,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,109.14) --
	(101.57,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.57,111.94) --
	( 99.86,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 99.86,109.14) --
	( 99.86,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,277.16) --
	(107.95,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.95,279.96) --
	( 95.41,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.41,277.16) --
	( 95.41,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,249.16) --
	(113.09,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.09,251.96) --
	(106.23,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.23,249.16) --
	(106.23,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,221.16) --
	(116.20,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.20,223.96) --
	(107.84,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (107.84,221.16) --
	(107.84,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,193.15) --
	(129.00,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.00,195.95) --
	(124.23,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.23,193.15) --
	(124.23,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,165.15) --
	(109.13,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.13,167.95) --
	(103.61,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (103.61,165.15) --
	(103.61,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 81.14) --
	(126.00, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.00, 83.94) --
	(120.97, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (120.97, 81.14) --
	(120.97, 86.74);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (102.86,139.95) circle (  3.57);

\path[fill=fillColor] (102.91,447.98) circle (  3.57);

\path[fill=fillColor] ( 97.61,419.98) circle (  3.57);

\path[fill=fillColor] ( 85.98,363.97) circle (  1.43);

\path[fill=fillColor] ( 92.52,335.97) circle (  3.57);

\path[fill=fillColor] ( 93.32,307.96) circle (  3.57);

\path[fill=fillColor] (100.71,111.94) circle (  3.57);

\path[fill=fillColor] (101.68,279.96) circle (  3.57);

\path[fill=fillColor] (109.66,251.96) circle (  3.57);

\path[fill=fillColor] (112.02,223.96) circle (  3.57);

\path[fill=fillColor] (126.59,195.95) circle (  3.57);

\path[fill=fillColor] (106.34,167.95) circle (  3.57);

\path[fill=fillColor] (123.48, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (152.13, 67.14) --
	(152.13,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (165.53, 67.14) --
	(165.53,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (178.92, 67.14) --
	(178.92,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (192.32, 67.14) --
	(192.32,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (145.43, 67.14) --
	(145.43,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.83, 67.14) --
	(158.83,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.22, 67.14) --
	(172.22,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.62, 67.14) --
	(185.62,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,137.15) --
	(159.63,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.63,139.95) --
	(150.10,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.10,137.15) --
	(150.10,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,445.18) --
	(151.33,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.33,447.98) --
	(148.11,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (148.11,445.18) --
	(148.11,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,417.18) --
	(157.97,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.97,419.98) --
	(152.24,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.24,417.18) --
	(152.24,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.17,361.17) --
	(154.17,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,333.17) --
	(161.72,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.72,335.97) --
	(157.11,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.11,333.17) --
	(157.11,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,305.16) --
	(161.19,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.19,307.96) --
	(153.10,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.10,305.16) --
	(153.10,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,109.14) --
	(153.52,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.52,111.94) --
	(152.29,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.29,109.14) --
	(152.29,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,277.16) --
	(154.70,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.70,279.96) --
	(146.93,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.93,277.16) --
	(146.93,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,249.16) --
	(169.12,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.12,251.96) --
	(162.37,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.37,249.16) --
	(162.37,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,165.15) --
	(153.04,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.04,167.95) --
	(149.24,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.24,165.15) --
	(149.24,170.75);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (154.86,139.95) circle (  3.57);

\path[fill=fillColor] (149.72,447.98) circle (  3.57);

\path[fill=fillColor] (155.13,419.98) circle (  3.57);

\path[fill=fillColor] (149.67,363.97) circle (  1.43);

\path[fill=fillColor] (159.42,335.97) circle (  3.57);

\path[fill=fillColor] (157.17,307.96) circle (  3.57);

\path[fill=fillColor] (152.88,111.94) circle (  3.57);

\path[fill=fillColor] (150.85,279.96) circle (  3.57);

\path[fill=fillColor] (165.74,251.96) circle (  3.57);

\path[fill=fillColor] (151.17,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (216.57, 67.14) --
	(216.57,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (229.96, 67.14) --
	(229.96,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (243.36, 67.14) --
	(243.36,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (256.76, 67.14) --
	(256.76,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (209.87, 67.14) --
	(209.87,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (223.27, 67.14) --
	(223.27,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (236.66, 67.14) --
	(236.66,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.06, 67.14) --
	(250.06,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,137.15) --
	(219.95,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (219.95,139.95) --
	(213.30,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.30,137.15) --
	(213.30,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,445.18) --
	(215.34,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.34,447.98) --
	(212.28,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.28,445.18) --
	(212.28,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,417.18) --
	(216.30,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.30,419.98) --
	(211.96,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.96,417.18) --
	(211.96,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,389.17) --
	(213.14,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,361.17) --
	(228.14,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.14,363.97) --
	(213.46,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.46,361.17) --
	(213.46,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,333.17) --
	(220.27,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.27,335.97) --
	(216.46,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.46,333.17) --
	(216.46,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,305.16) --
	(230.18,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.18,307.96) --
	(221.07,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.07,305.16) --
	(221.07,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,109.14) --
	(213.14,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.14,111.94) --
	(212.34,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,109.14) --
	(212.34,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,277.16) --
	(224.93,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.93,279.96) --
	(214.86,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.86,277.16) --
	(214.86,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,249.16) --
	(220.16,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.16,251.96) --
	(215.28,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.28,249.16) --
	(215.28,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,193.15) --
	(213.03,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.03,195.95) --
	(210.78,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.78,193.15) --
	(210.78,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,165.15) --
	(213.78,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.78,167.95) --
	(211.32,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.32,165.15) --
	(211.32,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 81.14) --
	(233.98, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (233.98, 83.94) --
	(227.82, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (227.82, 81.14) --
	(227.82, 86.74);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (216.62,139.95) circle (  3.57);

\path[fill=fillColor] (213.84,447.98) circle (  3.57);

\path[fill=fillColor] (214.16,419.98) circle (  3.57);

\path[fill=fillColor] (211.32,391.97) circle (  1.43);

\path[fill=fillColor] (220.80,363.97) circle (  3.57);

\path[fill=fillColor] (218.39,335.97) circle (  3.57);

\path[fill=fillColor] (225.62,307.96) circle (  3.57);

\path[fill=fillColor] (212.77,111.94) circle (  3.57);

\path[fill=fillColor] (219.89,279.96) circle (  3.57);

\path[fill=fillColor] (217.70,251.96) circle (  3.57);

\path[fill=fillColor] (211.91,195.95) circle (  3.57);

\path[fill=fillColor] (212.55,167.95) circle (  3.57);

>>>>

% Created by tikzDevice version 0.12.3.1 on 2021-05-04 13:12:53
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] ( 88.61, 67.14) --
	( 88.61,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (101.74, 67.14) --
	(101.74,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (114.88, 67.14) --
	(114.88,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (128.01, 67.14) --
	(128.01,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.05, 67.14) --
	( 82.05,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.18, 67.14) --
	( 95.18,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.31, 67.14) --
	(108.31,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.44, 67.14) --
	(121.44,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.62,137.15) --
	(111.62,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (111.62,139.95) --
	( 95.34,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.34,137.15) --
	( 95.34,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.37,445.18) --
	(106.37,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.37,447.98) --
	(100.69,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.69,445.18) --
	(100.69,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.80,417.18) --
	(101.80,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (101.80,419.98) --
	( 94.86,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 94.86,417.18) --
	( 94.86,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.61,361.17) --
	( 91.61,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.61,363.97) --
	( 82.20,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 82.20,361.17) --
	( 82.20,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.44,333.17) --
	( 95.44,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 95.44,335.97) --
	( 91.24,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 91.24,333.17) --
	( 91.24,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.23,305.16) --
	( 98.23,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 98.23,307.96) --
	( 89.98,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 89.98,305.16) --
	( 89.98,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.22,109.14) --
	(102.22,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (102.22,111.94) --
	(100.54,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (100.54,109.14) --
	(100.54,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.47,277.16) --
	(108.47,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.47,279.96) --
	( 96.18,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 96.18,277.16) --
	( 96.18,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.51,249.16) --
	(113.51,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (113.51,251.96) --
	(106.79,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (106.79,249.16) --
	(106.79,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.56,221.16) --
	(116.56,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (116.56,223.96) --
	(108.36,223.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (108.36,221.16) --
	(108.36,226.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.11,193.15) --
	(129.11,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (129.11,195.95) --
	(124.44,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (124.44,193.15) --
	(124.44,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.62,165.15) --
	(109.62,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (109.62,167.95) --
	(104.21,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (104.21,165.15) --
	(104.21,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.17, 81.14) --
	(126.17, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (126.17, 83.94) --
	(121.23, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (121.23, 81.14) --
	(121.23, 86.74);
\definecolor{fillColor}{RGB}{204,102,119}

\path[fill=fillColor] (103.48,139.95) circle (  3.57);

\path[fill=fillColor] (103.53,447.98) circle (  3.57);

\path[fill=fillColor] ( 98.33,419.98) circle (  3.57);

\path[fill=fillColor] ( 86.93,363.97) circle (  1.43);

\path[fill=fillColor] ( 93.34,335.97) circle (  3.57);

\path[fill=fillColor] ( 94.13,307.96) circle (  3.57);

\path[fill=fillColor] (101.38,111.94) circle (  3.57);

\path[fill=fillColor] (102.32,279.96) circle (  3.57);

\path[fill=fillColor] (110.15,251.96) circle (  3.57);

\path[fill=fillColor] (112.46,223.96) circle (  3.57);

\path[fill=fillColor] (126.75,195.95) circle (  3.57);

\path[fill=fillColor] (106.89,167.95) circle (  3.57);

\path[fill=fillColor] (123.70, 83.94) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (153.05, 67.14) --
	(153.05,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (166.18, 67.14) --
	(166.18,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (179.32, 67.14) --
	(179.32,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (192.45, 67.14) --
	(192.45,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.48, 67.14) --
	(146.48,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (159.62, 67.14) --
	(159.62,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (172.75, 67.14) --
	(172.75,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (185.88, 67.14) --
	(185.88,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.40,137.15) --
	(160.40,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (160.40,139.95) --
	(151.05,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (151.05,137.15) --
	(151.05,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.26,445.18) --
	(152.26,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (152.26,447.98) --
	(149.11,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (149.11,445.18) --
	(149.11,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.78,417.18) --
	(158.78,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (158.78,419.98) --
	(153.16,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.16,417.18) --
	(153.16,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.05,361.17) --
	(155.05,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.05,363.97) --
	(146.27,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (146.27,361.17) --
	(146.27,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.45,333.17) --
	(162.45,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (162.45,335.97) --
	(157.94,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (157.94,333.17) --
	(157.94,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.93,305.16) --
	(161.93,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (161.93,307.96) --
	(154.00,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.00,305.16) --
	(154.00,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.42,109.14) --
	(154.42,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (154.42,111.94) --
	(153.21,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.21,109.14) --
	(153.21,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.57,277.16) --
	(155.57,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (155.57,279.96) --
	(147.96,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (147.96,277.16) --
	(147.96,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.70,249.16) --
	(169.70,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (169.70,251.96) --
	(163.08,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (163.08,249.16) --
	(163.08,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.94,165.15) --
	(153.94,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (153.94,167.95) --
	(150.21,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (150.21,165.15) --
	(150.21,170.75);
\definecolor{fillColor}{RGB}{221,204,119}

\path[fill=fillColor] (155.73,139.95) circle (  3.57);

\path[fill=fillColor] (150.69,447.98) circle (  3.57);

\path[fill=fillColor] (155.99,419.98) circle (  3.57);

\path[fill=fillColor] (150.63,363.97) circle (  1.43);

\path[fill=fillColor] (160.19,335.97) circle (  3.57);

\path[fill=fillColor] (157.99,307.96) circle (  3.57);

\path[fill=fillColor] (153.79,111.94) circle (  3.57);

\path[fill=fillColor] (151.79,279.96) circle (  3.57);

\path[fill=fillColor] (166.39,251.96) circle (  3.57);

\path[fill=fillColor] (152.11,167.95) circle (  3.57);
\definecolor{drawColor}{RGB}{169,169,169}

@@

\path[draw=drawColor,line width= 0.3pt,line join=round] (217.49, 67.14) --
	(217.49,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (230.62, 67.14) --
	(230.62,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (243.75, 67.14) --
	(243.75,464.78);

\path[draw=drawColor,line width= 0.3pt,line join=round] (256.89, 67.14) --
	(256.89,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.92, 67.14) --
	(210.92,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (224.06, 67.14) --
	(224.06,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (237.19, 67.14) --
	(237.19,464.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (250.32, 67.14) --
	(250.32,464.78);

@@

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.80,137.15) --
	(220.80,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (220.80,139.95) --
	(214.28,139.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.28,137.15) --
	(214.28,142.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.28,445.18) --
	(216.28,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.28,447.98) --
	(213.29,447.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.29,445.18) --
	(213.29,450.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.23,417.18) --
	(217.23,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.23,419.98) --
	(212.97,419.98);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.97,417.18) --
	(212.97,422.78);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,389.17) --
	(214.13,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,391.97) --
	(210.56,391.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (210.56,389.17) --
	(210.56,394.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.84,361.17) --
	(228.84,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.84,363.97) --
	(214.44,363.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.44,361.17) --
	(214.44,366.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.11,333.17) --
	(221.11,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.11,335.97) --
	(217.38,335.97);

\path[draw=drawColor,line width= 0.6pt,line join=round] (217.38,333.17) --
	(217.38,338.77);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.83,305.16) --
	(230.83,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (230.83,307.96) --
	(221.90,307.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.90,305.16) --
	(221.90,310.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,109.14) --
	(214.13,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.13,111.94) --
	(213.34,111.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (213.34,109.14) --
	(213.34,114.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.68,277.16) --
	(225.68,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (225.68,279.96) --
	(215.81,279.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (215.81,277.16) --
	(215.81,282.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.01,249.16) --
	(221.01,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (221.01,251.96) --
	(216.23,251.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] (216.23,249.16) --
	(216.23,254.76);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.02,193.15) --
	(214.02,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.02,195.95) --
	(211.82,195.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (211.82,193.15) --
	(211.82,198.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.76,165.15) --
	(214.76,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (214.76,167.95) --
	(212.34,167.95);

\path[draw=drawColor,line width= 0.6pt,line join=round] (212.34,165.15) --
	(212.34,170.75);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.56, 81.14) --
	(234.56, 86.74);

\path[draw=drawColor,line width= 0.6pt,line join=round] (234.56, 83.94) --
	(228.52, 83.94);

\path[draw=drawColor,line width= 0.6pt,line join=round] (228.52, 81.14) --
	(228.52, 86.74);
\definecolor{fillColor}{RGB}{17,119,51}

\path[fill=fillColor] (217.54,139.95) circle (  3.57);

\path[fill=fillColor] (214.81,447.98) circle (  3.57);

\path[fill=fillColor] (215.13,419.98) circle (  3.57);

\path[fill=fillColor] (212.34,391.97) circle (  1.43);

\path[fill=fillColor] (221.64,363.97) circle (  3.57);

\path[fill=fillColor] (219.28,335.97) circle (  3.57);

\path[fill=fillColor] (226.37,307.96) circle (  3.57);

\path[fill=fillColor] (213.76,111.94) circle (  3.57);

\path[fill=fillColor] (220.75,279.96) circle (  3.57);
